Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654

### 2016-03-29 WRITEUP/Intro.tex
combine with Lensmodel.tex

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
% set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
% combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.654
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations.  The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17.9 km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
discarding 
unusable visibility data. 
The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary
absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks. 
The phase calibrator J1127-189 from the first track is faint and observed under
poor weather and the phase calibrator 3C273 is far from source for the second
track. Hence, the phase calibration was 
subpar, with rms scatter $\sim$ 60\degr, 
yielding
$\sim
$BLAH\% calibration accuracy.
% flux scale uncertainty
% gain variation over time
% phase scatter 
%
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final 
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

@@

\end{document}

>>>>

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
% set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
% combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) 
%toward the background galaxy RXJ1131-1231 at $z$ = 0.654
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) on 2014 February 17 
under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations.  The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17.9 km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
flagging poor visibility data. 
The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary
absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks. 
% poor phase note
Since the phase calibrator from the first track is faint and was observed under
poor weather and the phase calibrator used for the second track was
far from our target source.
Hence, the phase calibration was 
subpar, with rms scatter $\sim$ 60\degr. 
We estimate $\sim
$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and 
the calibrated phase scatter.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final 
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

@@

\section{\rot{2}{1} Lens model}

\subsection{interpretation}
- C06 suggest the presence of an interacting dusty galaxy in their HST
observations, which BJB+08 calls it the F component. The lensed images of the
ABCDE 
components coincide with our CO data (see mom0 on HST and channel map),
evidently CO emission coming from the AGN host galaxy. 
- one of the red channels in our lens model suggests a second source component,
which is consistent with the spatially offset dusty source (see mom0 on HST,
which 
the red velocity component coincides with this F component)

%%%%%%%%%%%%%%%%%%%%%%%%
We compare our lens model parameters on the mass distribution of the lensing
galaxy with literature, particularly against the SIE model presented by C06. 
In C06, their SIE model shows position of lensing mass is offset by (-0.015",
-0.041" from obsservations (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
theta\_R = 1.84" $\pm$ 0.01. 
Our best-fit model parameters finds a BLAH
	- Our model lens parameters (median):
		- file: WRITEUP/MedianLensModelParams.txt
		- lensing gal. position is consistent with C06, 
		- Einstein radius: consistent with C06
		- PA: consistent within errors
		- Axial ratio: consistent within errors
%%%%%%%%%%%%%%%%%%%%%%%%%

Differential lensing is at play as suggested by the spectral shape of the \rot{2}{1} line profile, where 
flux density in the red wing is much high than in the blue wing.  
We modelled the emission using different kinematic components, the magnification factors are reported in Table BLAH.
\input{table_magFactor}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
\caption{
Pseudo observed 0th moment map in the lens plane. (left)
Pseudo 0th moment map in the source plane. (right)
\label{fig:}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.65\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.65\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
of channel widths $\sim$ 100\kms. 
\label{fig:}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
\caption{
velocity gradient of the lens model in the lens plane (left), source plane
(right).
\label{fig:}}
\end{figure}

%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{}
%\includegraphics[width=0.65\textwidth]{}
%\caption{
%\label{fig:}}
%\end{figure*}
\end{document}
